### 2017-12-05 manuscript.rmd
added mantle canal characters

@@

```{r simmap_making, echo=F, message=F, warning=F, include=F}
#Stochastic trait mapping:
#Make simmap objects
#print("SIMMAP Sex Distribution")
make.simmap(ultratree, sex, nsim = 100, message=FALSE) -> sex_sim
#print("SIMMAP Palpons")
make.simmap(ultratree, palpons, nsim = 100, message=FALSE) -> palpons_sim
#print("SIMMAP Tentilla")
make.simmap(ultratree, tentilla, nsim = 100, message=FALSE) -> tentilla_sim
#print("SIMMAP Tentilla2")
make.simmap(ultratree, tentilla2, nsim = 100, message=FALSE) -> tentilla_sim2
#print("SIMMAP Nectosome")
make.simmap(ultratree, nectosome, nsim = 100, message=FALSE) -> nectosome_sim
#print("SIMMAP Nectosome Position")
make.simmap(ultratree, bracts, nsim = 100) -> bracts_sim
#print("SIMMAP Habitat")

@@

>>>>

mantle = cdata$Mantle.Canal
names(mantle)=rownames(cdata)
mantle[is.na(mantle)]=0

@@

```{r simmap_making, echo=F, message=F, warning=F, include=F}
#Stochastic trait mapping:
#Make simmap objects
#print("SIMMAP Sex Distribution")
make.simmap(ultratree, sex, nsim = 100, message=FALSE) -> sex_sim
#print("SIMMAP Palpons")
make.simmap(ultratree, palpons, nsim = 100, message=FALSE) -> palpons_sim
#print("SIMMAP Tentilla")
make.simmap(ultratree, tentilla, nsim = 100, message=FALSE) -> tentilla_sim
#print("SIMMAP Tentilla2")
make.simmap(ultratree, tentilla2, nsim = 100, message=FALSE) -> tentilla_sim2
#print("SIMMAP Nectosome")
make.simmap(ultratree, nectosome, nsim = 100, message=FALSE) -> nectosome_sim
#print("SIMMAP Nectosome Position")
make.simmap(ultratree, bracts, nsim = 100, message=FALSE) -> bracts_sim
#print("SIMMAP Habitat")
make.simmap(ultratree, mantle, nsim = 100, message=FALSE) -> mantle_sim

@@

```{r mantle, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome"}
#Simmap NECTOSOME
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(mantle_sim)
```
